\input{modules/templates/experience.tex}

\newcommand{\experience}{
    \section*{Experience}
    \bluesubsection{Schrödinger}
    \experienceCreator{Senior Developer I}{January 2026 - Present}
        \begin{itemize}
            \item Project lead of Maestro Assistant.
            \item Developed a Semantic Panel Search prototype using vector embeddings to replace legacy algorithmic search, successfully validating the architecture for production deployment
            \item Collaborating on architecture design of Notification and Authentication services for Maestro.
        \end{itemize}
    
    \experienceCreator{Developer II}{July 2024 - December 2025}
        \begin{itemize}
            \item Engineered the "Maestro Assistant" service into a single proxy, implementing CI/CD pipelines and telemetry to support 100+ daily production requests. Recieved recognition from company leadership and customers like BMS, GSK.
            \item Implemented non-bonded interaction calculation library; a modular C++ library with caching. It reduced the calculation time by 300-400x; cut 10-min tasks to 30s.
            \item Mentored an engineering intern on the Project Table Calculator, implementing daily code reviews and enforcing scalable design patterns to ensure the successful delivery of major project components. 
        \end{itemize}
        
    \experienceCreator{Developer I}{June 2023 - June 2024}
        \begin{itemize}
            \item Refactored 2000+ lines of legacy code using Factory and Strategy patterns, improving extensibility for handling diverse Job Server outputs.
            \item Enhanced export functionality for new movie presets (e.g., View Ligand Docking) from Maestro to PyMOL, decreasing manual visualization setup time by 60\% and enhancing automated workflow efficiency.
        \end{itemize}
        
        \experienceCreator{Intern - Software Development}{January 2023 - May 2023}
        \begin{itemize}
            \item Created an adapter for Schrödinger’s structure class that removed the m2io dependency and enabled a property-writing mechanism with 3x greater flexibility, gaining recognition from Scientific Infrastructure team.
            \item Implemented a robust Find Toolbar widget following MVC pattern and command pattern with python and C++ inter communication.
        \end{itemize}

    \experienceCreator{Intern - Software Development}{May 2022 - July 2022}
        \begin{itemize}
            \item Delivered a robust preset management feature in 2 months—30\% faster thanaverage—using Factory and Adapter design patterns.
        \end{itemize}
}